
% acknowledgements for thesis

Thank you to Dr. Aaron Becker, for giving me the opportunity to work on these wonderful projects, with these interesting people.
You are a wonderful example of a professor who cares about his student and his teaching as much as his research.
I hope the lab continue to grow after I graduate.
I hope I graduate.
Thank you to the lab members who came and went during my time here, for putting up with me.
Thank you for allowing me to be a lab manager my way, even though it might not have been the most friendly way.
I hope you are able to utilize this lab we have built together for a long time.
%Thank you to the Master students from our lab who came before me, to show me that it is possible.
%Thank you to the our lab's undergraduate students, some of you have become Master students with me.
%Should jazz this up a bit

Thank you to my collaborators, who put up with me when, by my own choice, I worked alone on our collaboration.

Thank you to my parents, Tung Thanh Trinh and Binh Van Nguyen, and my sister, Duong Thuy Nguyen.
Mom, you sacrificed your professional and social life for our family.
I regret not being able to spend as much time with you when I was in school, hopefully that will change soon.
Dad, your stories of the bad times showed me that it can work out if I keep going, and with a little bit of luck, or the ancestors' blessing, as you put it.
Thank you for giving us a better life, and the opportunity to do what I love.
I hope I can be proud of myself as you are of me.
I hope I give you guys less headache.
Duong, thank you for showing me that you don't have to be successful in school to be successful in life.
I wish you and Juan to be happy and fulfilled the rest of your life, and am grateful you decide to share that happiness with me.
